Consensus cell types across samples from brain and CNS tumors

### 2025-02-12 analyses/cell-type-consensus/exploratory-notebooks/04-brain-and-cns-consensus-celltypes.Rmd
Apply suggestions from code review
Co-authored-by: Jaclyn Taroni <19534205+jaclyn-taroni@users.noreply.github.com>
some rewording

## Macrophage vs. T cell populations

It looks like there may be some differences between T cell and macrophage infiltrate based on the tumor type. 
Here we will look specifically at all T cells and anything in the macrophage/monocyte lineage. 
I'm including any cell types that are in our list of possible cell types and a child of [mononuclear phagocyte](https://www.ebi.ac.uk/ols4/ontologies/cl/classes/http%253A%252F%252Fpurl.obolibrary.org%252Fobo%252FCL_0000113?lang=en) in the macro/mono group. 
We should also note that "macrophage" here probably refers to microglia instead.

@@

- As expected based on the previous plot, glioblastoma appears to have greater T cell infiltrate than macrophages across all samples. 
- There appears to be a handful of samples in the "High-grade glioma" group that also have high T cell infiltrate. 
Notably, glioblastoma is a type of HGG. 
- Generally, the T cell population seems lowest in LGG. 
Ganglioglioma also has fewer samples with high percentage of T cell infiltrate and this is also a LGG. 
- It looks like about 50% of the pilocytic astrocytomas have more T cell infiltrate than macrophages.

@@

Consistent with the previous findings it looks like HGG tend to have higher T cell infiltrate while LGG tend to have higher macrophage infiltrate.

>>>>

## Myeloid vs. T cell populations

It looks like there may be some differences between the presence of T cells and macrophages based on the tumor type. 
Here we will look specifically at all T cells and anything in the myeloid lineage, which includes macrophages, monocytes, mononuclear phagocytes, myeloid leukoctyes, and neutrophils. 
We should also note that "macrophage" here probably refers to microglia instead.

@@

- As expected based on the previous plot, glioblastoma appears to have a higher proportion of T cells when compared to myleoid cells across all samples. 
- There appears to be a handful of samples in the "High-grade glioma" group that also have high T cell infiltrate. 
Notably, glioblastoma is a type of HGG. 
- Generally, the T cell population seems lowest in LGG. 
Ganglioglioma also has fewer samples with high percentage of T cell infiltrate and this is also a LGG. 
- It looks like about 50% of the pilocytic astrocytomas have more T cells than myeloid cells.

@@

Consistent with the previous findings it looks like HGG tend to have a higher proportion of T cells while LGG tend to have higher myeloid cell proportions.
